\vspace{-2.5cm}A generative model for urban firm networks

### 2020-09-16 communications/NetSci2020/slidesNetSci.tex

\title[Agent-based modeling city networks]{An agent-based model for city networks based on interactions between firms}
\author[Raimbault \and Zdanowska]{J.~Raimbault$^{1,2,3\ast}$ \and N. Zdanowska$^{1,3}$\\\medskip
$^{\ast}$\texttt{j.raimbault@ucl.ac.uk}
}

@@

\date[2nd October 2019]{CCS 2019\\
Satellite Simulation models\\
October 2nd 2019
}

@@

\begin{itemize}
    \item Cities as cross-overs of socio-economic interactions 
    \item Network economies \cite{sassen1991global} \cite{castells1996information}
    \item World city network driven by interactions between firms \cite{taylor2001specification} \cite{martinus2018global}
    \item Asymmetrical spatial interactions -- different relative position of cities
\end{itemize}

@@

\begin{itemize}
    \item Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}
    \item Adaptive cycles and diffusion on innovation \cite{Hagerstrand1968Innovation}
    \item Path dependence \cite{martin2006path} \cite{pumain2012urban}
    \item Selection and emerging structures of systems % pas clair
    \item Evolutionary models for urban systems dynamics: \cite{favaro2011gibrat} \cite{cottineau2015growing} \cite{schmitt2015half} \cite{raimbault2018indirect} \cite{raimbault2018calibration}
\end{itemize}

@@

\sframe{Firm linkages structuring urban systems}{

 \begin{center}
 \includegraphics[width=0.7\textwidth]{figures/Figure1.png}
 \end{center}

  \textit{Central and Eastern European cities within ownership links of firms in 2013}

\sframe{Firm linkages structuring urban systems}{

 \begin{center}
 \includegraphics[width=0.7\textwidth]{figures/Figure2.jpg}
 \end{center}

  \textit{UK cities within transnational ownership links of firms in 2016}

% bon je ne sais pas si c'est utile mais au moins ca fait un exempple en plus (bon ok on ne voit rien)

@@

% j'ai mis ca plus pour moi,enfin pour moi c'est plus clair pour la presentation
%  => oui c'est exactement ce quil fallait mettre !
% question a la con, mais est-ce que ce n'est pas tautolgique de dire que les villes et les liens sont definis par le GDP, ou le lien est bien defini par le GDP des noeuds.
}

@@

% excuses-moi, mais je vais commencer a partir de la a te demander de m'expliquer, ca va te paraitre evident je suis desolee, mais c'est pour que je ne trompe pas en presentant
% a quoi correspond le i et j? En gros c'est ville i, puis la ville j? Le k c'est bien le nombre de secteurs? 
% -> oui exactement

@@

\sframe{Simulation of urban networks}{

    % examples

    \begin{center}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}
	\end{center}

@@

    \includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}

@@

     \includegraphics[width=0.48\textwidth]{figures/internationalization-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gammaSectors_errorbars.png}

@@

    \begin{center}
    \includegraphics[width=\textwidth]{figures/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

@@

    \begin{center}
    	\includegraphics[height=0.6\textheight]{figures/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

>>>>

\title
[A generative model for urban firm networks]{A generative model for urban firm networks}
\author[Raimbault \and Zdanowska \and Arcaute]{J.~Raimbault$^{1,2,3\ast}$ \and N. Zdanowska$^{1,3}$ \and E. Arcaute$^{1}$\\\medskip
$^{\ast}$\texttt{j.raimbault@ucl.ac.uk}
}

@@

\date[24 September 2020]{NetSci\\
September 24 2020
}

@@

\begin{itemize}
\item Cities as cross-overs of socio-economic interactions           \cite{castells1996information}
    \item Networks as the new social morphology of societies \cite{castells2000networksociety}, giving rise to network economies \cite{sassen1991global} 
    \item Emergence of an interconnected world city network as a crucial feature of globalisation 
    \item Interurban interactions between firms as one of the most representative of economic trends \cite{taylor2001specification} \cite{martinus2018global}

\end{itemize}

@@

\begin{itemize}
    \item Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}
    \item Adaptive cycles and diffusion of innovation \cite{Hagerstrand1968Innovation}
    \item Path dependence \cite{martin2006path} \cite{pumain2012urban}
    \item Selection and emerging structures of systems 
    \item Evolutionary models for urban systems dynamics: \cite{favaro2011gibrat} \cite{cottineau2015growing} \cite{schmitt2015half} \cite{raimbault2018indirect} \cite{raimbault2018calibration}
\end{itemize}

@@

@@

@@

% Le k c'est bien le nombre de secteurs? 
% -> oui exactement

@@

\sframe{Simulation of urban networks}

{
    % examples

    \begin{center}
    \includegraphics[width=0.48\textwidth]{figuresraw/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figuresraw/ex_alleq-lowgravity_seed-12102_t1500.png}
	\end{center}

@@

    \includegraphics[width=0.48\textwidth]{figuresraw/internationalisation-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figuresraw/rhoDegreeSize-gravityDecay_errorbars.png}

@@

     \includegraphics[width=0.48\textwidth]{figuresraw/internationalisation-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figuresraw/rhoDegreeSize-gammaSectors_errorbars.png}

@@

    \begin{center}
    \includegraphics[width=\textwidth]{figuresraw/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

@@

    \begin{center}
    	\includegraphics[height=0.6\textheight]{figuresraw/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}

    \end{center}
